Basic concepts and tools for the Toki Pona minimalist language: Wordnet synsets; analysis, synthesis and syntax highlighting of texts

### 2017-12-06 article/article.tex
advanced in text synthesis
arrumada sintese de poemas

\subsection{Synthesis of text}\label{synth}
Such counting exercises is also useful
for (semi-)automated writing through scripting.
The syntax organizes the words in larger structures.
The rhymes are restricted and sonorities are
restricted by the small vocabulary and simple syntax.
There are some specific tasks for achieving texts,
such as finding the number of syllables considering the elisions,
or handling interaction of the writer with the script
to choose sentences or verses or stanzas.

The same package~\cite{tokipona}
has capabilities for synthesizing Toki Pona text.
Noun, verb and prepositional phrases,
sentences.
It also aims at making larger scale texts
by keeping a record of the used words and structures (context)
and using stylistic outlines for poems and short narratives.

@@

@@

>>>>

\subsection{Synthesis of text}\label{synth}
Such counting exercises are also useful
for facilitating (semi-)automated writing through scripting.
The syntax organizes the words in larger structures.
The rhymes are restricted and sonorities are
restricted by the small vocabulary and simple syntax.
There are some specific tasks for achieving texts,
such as finding the number of syllables considering the elisions,
or handling interaction of the writer with the script
to choose sentences or verses or stanzas.

The same package~\cite{tokipona}
has capabilities for synthesizing Toki Pona text.
On its most basic level, the routines yield
noun, verb and prepositional phrases,
sentences.
They also aim at making larger scale texts
by keeping a record of the used words and structures (context)
and using stylistic outlines for poems and short narratives.

@@

Automatic and randomic synthesis of texts in Toki Pona are
useful because of the reduced vocabulary: ideas often make
sense in unexpected way, and yield a way to 
explore the semantic field possible by Toki Pona.
Each words is related to a broad semantic field,
thus the randomized selection of words are more likely
to make sense.
One might object that the resulting texts are unusual 
and even consider that they often hold insubstantial or unsound meaning.
We advocate that these unexpected formations are desirable
for exploring the possibilities of the language and of thought,
and for artistic endeavors.
Also, to obtain texts which one finds usual or satisfactory
in more strict or personal terms, such a person might just write
them normally.

% phrase
% sentence
% poem
% text
% each with a different color scheme

@@

% :TOhtml command
